Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-28 analysis/paper/paper.qmd
Fixed error by trying this --> https://github.com/r-spatial/sf/issues/1762

veg_all <- read_sf(here("analysis/data/gis_data/eco_region.shp"))

veg_all <- st_transform(veg_all, crs = st_crs(4162))

@@

pts_all <- st_as_sf(korean_archaeological_site_locations_tcsa,
                coords = c(   "long_dd.y", "lat_dd.y"),
                crs = st_crs(veg_all))
ggplot() +
  geom_sf(data = pts_all)

>>>>

veg_all <- read_sf(here("analysis/data/gis_data/eco_re_two.shp"))

veg_all <- st_transform(veg_all, crs = st_crs(4326))

@@

pts_all <- st_as_sf(korean_archaeological_site_locations_tcsa,
                coords = c("long_dd.y", "lat_dd.y"),
                crs = st_crs(veg_all))
ggplot() +
  geom_sf(data = pts_all)

#sf_use_s2(FALSE)
